Light inextensible strings (thread) under tension in the Schwarzschild geometry

### 2021-03-12 tpe_edreview2_rebuttal.tex

and thus their difference is

\[
\ell_\mathrm{Sch} - \ell_\mathrm{flat}\sim M\log w
\]

which goes to infinity logarithmically; in other words, for an
infinite string the Schwarzschild metric is a ``worse infinity" which
diverges faster than what occurs in flat spacetime.  So far, so good.
I guess what bothers me is the statement that ``even far from [emphasis
  added] the event horizon, radial strings are arbitrarily longer than
flat space would imply...".  So long as $w$ is large (however far from
the event horizon) but finite, the lengths in both metrics are precise
numbers, not arbitrary.  Only when $w$ goes to infinity does the
length in Schwarzschild spacetime become infinitely longer than the
length in flat spacetime, although though both are infinite.  I
suppose this passage would sit better with this reader by merely
stating that the asymptotic difference between $\ell_\mathrm{Sch}$ and
$\ell_\mathrm{flat}$ diverges logarithmically.  But perhaps this is
only a matter of taste.

\textcolor{blue}{This is a subtle point which took me some
  considerable time to understand.  I would express the problem with
  the existing text as that the radial strings concerned stretch all
  the way to the event horizon; yet the phrase ``far from the event
  horizon'' kind of suggests that {\em all} the string is far from the
  event horizon.\\ It is possible to get round this informally by
  considering the proper length of a radial string from $2M(1+w_1)$ to
  $2M(1+w_2)$ (where we understand $2M\leq w_1\leq w_2$), which is seen from
  equation 4 to be $2M(w_1-w_2 + \log\left(\frac{w_2}{w_1}\right) +
  O(w_1^{-1})$.\\ But on balance this is a rather unspectacular result
  which would require a distractingly large amount of explanation.  On
  balance I think it best to leave this out, resulting, I hope in
  sharper, more focussed wording.
\\ {\bf old text}
The discrepancy\ldots has the startling feature that
$\lim_{w\longrightarrow\infty}\Delta=\infty$ (because of the $\log w$
term).  This suggests that, even far from the event horizon, radial
strings are arbitrarily longer than flat space would imply: a nice
illustration of the failure of Euclidean geometry.
\\ {\bf new text}
The discrepancy\ldots has the startling feature that
$\lim_{w\longrightarrow\infty}\Delta=\infty$ (because of the $\log w$
term): a nice illustration of the failure of Euclidean geometry.
}

### 2021-03-12 string_physics_educator_revision4.tex
work on another comment

\noindent The discrepancy $\Delta=\ell-2Mw$ between the flat-space result of $2Mw$ and
equation~\ref{asymptotic_ell} has the startling feature that $\lim_{w\longrightarrow\infty}\Delta=\infty$ (because of the $\log w$ term).  This suggests that, even far from the event
horizon, radial strings are arbitrarily longer than flat space would
imply: a nice illustration of the failure of Euclidean geometry.
Again taking a solar mass black hole but with $w=2\times 10^7$
(corresponding to the orbital radius of Mercury) the difference
between the classical result and equation~\ref{asymptotic_ell} is
about $28\,\mathrm{km}$ of extra string.  However, the prediction is
unlikely to be the basis of a fourth test of general relativity---the
others being Shapiro time delay, bending of starlight, and the
perihelion advance of Mercury~\cite{einstein1916}---as the Sun is not
inside its own Schwarzschild radius.

>>>>

\noindent The discrepancy $\Delta=\ell-2Mw$ between the flat-space result of $2Mw$ and
equation~\ref{asymptotic_ell} has the startling feature that $\lim_{w\longrightarrow\infty}\Delta=\infty$ (because of the $\log w$ term): a nice illustration of the failure of Euclidean geometry.
Again taking a solar mass black hole but with $w=2\times 10^7$
(corresponding to the orbital radius of Mercury) the difference
between the classical result and equation~\ref{asymptotic_ell} is
about $28\,\mathrm{km}$ of extra string.  However, the prediction is
unlikely to be the basis of a fourth test of general relativity---the
others being Shapiro time delay, bending of starlight, and the
perihelion advance of Mercury~\cite{einstein1916}---as the Sun is not
inside its own Schwarzschild radius.
